---
title: 'Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere'
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    pdf_document:
        toc: true
header-includes:
      - \usepackage{float}
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{booktabs}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE)

# If `DCPOtools` is not yet installed:
# remotes::install_github("fsolt/DCPOtools")

library(DCPOtools)
library(DCPO)
library(tidyverse)
library(glue)
library(countrycode)
library(patchwork)
library(modelsummary)

set.seed(324)
```

# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism 

```{r pge_items}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_output.rda"))

dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")

process_dcpo_input_raw <- function(dcpo_input_raw_df) {
  dcpo_input_raw_df %>% 
  DCPOtools::with_min_yrs(2) %>% 
  DCPOtools::with_min_cy(5) %>% 
  group_by(country) %>% 
  mutate(cc_rank = n()) %>% 
  ungroup() %>% 
  arrange(-cc_rank)
} 

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)

pge_items <- read_csv(here::here("data-raw", "egr_questions.csv"),
                      col_types = "cccccc")

alpha_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "alpha") %>% 
    transmute(item = question,
              dispersion = mean)

beta_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "beta") %>% 
    group_by(question) %>% 
    summarize(difficulties0 = paste0(round(mean, 2), collapse = ", ")) %>% 
    mutate(item = question,
           cp = as.numeric(str_extract(item, "\\d")) - 1,
           term = str_glue("(( ?-?[0-9].[0-9][0-9]?,?){{{cp}}})"),
           difficulties = str_extract(difficulties0, 
                                      term) %>%
               str_replace(",$", "") %>% 
               str_trim()) %>% 
    transmute(item, difficulties)
                                    
items_summary <- dcpo_input_raw_public1 %>%
    dplyr::select(country, year, item, survey) %>%
    distinct() %>%
    separate(survey, c("surv1", "surv2", "surv3"), sep=", ", fill = "left") %>%
    pivot_longer(cols = starts_with("surv"), values_to = "survey") %>%
    filter(!is.na(survey)) %>% 
    group_by(item, survey) %>% 
    summarize(n_cy = n()) %>% 
    arrange(item, -n_cy) %>% 
    group_by(item) %>% 
    mutate(total_cy = sum(n_cy),
           all_surveys = paste0(survey, collapse = ", ")) %>% 
    slice(1) %>% 
    ungroup() %>% 
    left_join(pge_items %>% select(item, survey, question_text),
              by = c("item", "survey")) %>% 
    left_join(alpha_results, by = "item") %>% 
    left_join(beta_results, by = "item") %>% 
    arrange(-total_cy) %>% 
    select(-survey, -n_cy)
```

```{r pge_items_table1}    
items_summary[1:9,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```


```{r pge_items_table2}    
items_summary[10:17,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table3}    
items_summary[18:27,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table4}    
items_summary[28:34,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table5}    
items_summary[35:46,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table6}    
items_summary[47:49,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
              `Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra",
                                 note = "") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

\vspace{-.45in}
Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found in the cross-national survey dataset.  Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.  Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.  Survey dataset codes correspond to those used in the `DCPOtools` package.
